
\begin{thebibliography}{99}
\addcontentsline{toc}{section}{Bibliography}

\bibitem{Babuska}Babuska I., Práger M., Vitásek E.: {\em Numerical Processes in Differential Equations}, STNL Praha - Wiley, 1966.

 \bibitem{demk1}
Demkowicz L., Oden J.T., Rachowicz W., Hardy O.:
Toward a universal $hp$-adaptive finite element strategy.
Part 1: constrained approximation and data structure.
Comput. Methods Appl. Math. Engrg., \textbf{77}, 79 - 112, 1989.

\bibitem{cerveny}
Èervený, J., higher-order adaptive FEM for non-linear coupled problems, Department of Mathematical Sciences, The University of Texas at El Paso, 2007

\bibitem{derade}
Demkowicz L., Rachowicz W., Devloo P.: A Fully Automatic $hp$-Adaptivity. TICAM Report
No. 01-28, University of Texas at Austin, 2001.

\bibitem{dubcova}
L. Dubcova, P. Solin, J. Cerveny, P. Kus: Space and Time Adaptive Two-Mesh hp-FEM for Transient 
Microwave Heating Problems, Electromagnetics, Vol. 30, Issue 1, pp. 23 - 40, 2010.

\bibitem{DF04}Dolejsi V., Feistauer M.: {\em A semi-implicit discontinuous Gelerkin finite element method for the numerical solution of inviscid compressible flow}, J. Comput. Phys., \textbf{198}, 727 - 746, 2004.
 
 \bibitem{DFS03}Dolejsi V., Feistauer M., Schwab C.: {\em On some aspects of the discontinuous Galerkin finite element method for conservation laws}, Math. Comput. Simul., \textbf{6}, 333 - 346, 2003.

 \bibitem{1993}Feistauer M.: {\em Mathematical methods in fluid dynamics}, Longman Scientific \& Technical, 1993.

 \bibitem{compress}Feistauer M., Felcman J., Straskraba I.: {\em Mathematical and Computational Methods for Compressible Flow}, Oxford University Press, 2003.

 \bibitem{hyp06}Feistauer M., Kucera V.: {\em A New Technique for the Numerical Solution of the Compressible Euler Equations with Arbitrary Mach Numbers}, Proc. of the Conference Hyperbolic Problems:Theory, Numerics and Applications, Springer-Verlag Berlin-Heidelberg, 523 - 531, 2008.

\bibitem{hermes} Hermes, an open source C++ library for rapid development of 
adaptive $hp$-FEM and $hp$-DG codes with emphasis on nonlinear, time-dependent,
multiphysics coupled problems http://hpfem.org/hermes.

 \bibitem{Kuzmin}D. Kuzmin.: {\em A vertex-based hierarchical slope limiter for p-adaptive discontinuous Galerkin
methods}, J. Comput. Appl. Math., \textbf{233(12)}, 3077-3085, 2010.

\bibitem{SUPG}Lube G.:\emph{Stabilized Galerkin finite element methods for convection dominated and incompressible flow problems}, Num. Anal. and Math. Model. {\bf 29}, Banach Center publications, Warszawa, 1994.

\bibitem{multimesh1}
P. Solin, J. Cerveny, L. Dubcova, D. Andrs: Monolithic Discretization of Linear Thermoelasticity Problems via Adaptive Multimesh hp-FEM, J. Comput. Appl. Math 234 (2010) 2350 - 2357.

\bibitem{multimesh2}
P. Solin, L. Dubcova, J. Kruis: Adaptive hp-FEM with Dynamical Meshes for Transient Heat and Moisture Transfer Problems, J. Comput. Appl. Math. 233 (2010) 3103-3112.

\bibitem{sosedo}
P. Solin, K. Segeth, I. Dolezel: {\em Higher-Order Finite Element Methods}, CRC Press, 2003.

\bibitem{karniadakis}
Karniadakis G.E., Sherwin S.J.: {\em Spectral/$hp$ Element Methods for CFD},
Oxford University Press, Oxford, 1999.

\bibitem{solin2}
Solin P.: Partial Differential Equations and the Finite Element Method, 
J. Wiley \& Sons, New Jersey, 2006

\bibitem{solin1}
Solin P., Segeth K. and Dolezel I.:
{\em Higher-Order Finite Element Methods},
Chapman \& Hall/CRC Press, Boca Raton, 2003.

\bibitem{reflected}
Tayfun E. Tezduyar, Masayoshi Senga:
Stabilization and shock-capturing parameters in SUPG formulation of compressible flows,
Comput. Methods Appl. Mech. Engrg. 195, 1621 – 1632, 2006

\end{thebibliography}
